\onecolumn

\section{Bibliography}

\hypertarget{ackerman}{Ackerman, Andy, ed. 1995. \emph{The Wink}. Seinfeld.}

\hypertarget{adams}{Adams, Carol J. 2010. \emph{The Sexual Politics of Meat (20th Anniversary Edition)}. New York, London: Continuum.}

\hypertarget{arganini}{Arganini, Claudia, Anna Saba, Raffaella Comitato, Fabio Virgili, and
 Aida Turrini. 2012. ``Gender Differences in Food Choice and Dietary
 Intake in Modern Western Societies.'' Pp. 83--102 in \emph{Public Health
  - Social and Behavioral Health}, edited by J. Maddock. Retrieved November 24, 2019 (\href{https://www.intechopen.com/books/public-health-social-and-behavioral-health/gender-differences-in-food-choice-and-dietary-intake-in-modern-western-societies}{https://www.intechopen.com/books/public-health-social-and-behavioral-health/gender-differences-in-food-choice-and-dietary-intake-in-modern-western-societies}).}

\hypertarget{aryanism}{2009. ``Veganism.'' \emph{Aryanism}. Retrieved May 2, 2019}
(\url{http://aryanism.net/culture/veganism/}).

\hypertarget{barber1}{Barber, Kristen. 2016. \emph{Styling Masculinity: Gender, Class, and Inequality in the Men's Grooming Industry}. 1st ed. New Brunswick, New Jersey: Rutgers University Press.}

\hypertarget{barber2}{Barber, Kristen. 2019. ``Styling Masculinity: Gender, Class, and Inequality in the Men's Grooming Industry, by Kristen Barber (Rutgers University Press, 2016).'' \emph{Pacific Sociological Association Annual Conference 2019} 1:30.}

\hypertarget{beck}{Beck, Julie. 2018. ``The Sad Ballad of Salad.'' \emph{The Atlantic}. Retrieved September 16, 2018 (\href{http://theatlantic.com/health/archive/2016/07/the-sad-ballad-of-salad/493274/}{theatlantic.com/health\\/archive/2016/07/the-sad-ballad-of-salad/493274/}).}

\hypertarget{bem}{Bem, Sandra L. 1974. ``The Measurement of Psychological Androgyny.'' \emph{Journal of Consulting and Clinical Psychology} 42(3):155--62.}

\hypertarget{boren}{Boren, Cindy and Des Bieler. 2019. ```We Have Everything That I Like': Trump Serves Fast-Food Feast for Clemson's White House Visit.'' \emph{Washington Post}. Retrieved April 26, 2019 (\url{https://www.washingtonpost.com/sports/2019/01/14/clemson-tigers-visit-white-house-meet-with-trump}).}

\hypertarget{brady}{Brady, Jennifer and Matthew Ventresca. 2014. ```Officially a Vegan Now.''' \emph{Food and Foodways} 22(4):300--321.}

\hypertarget{brubach}{Brubach, Holly. 2008. ``Real Men Eat Meat.'' \emph{New York Times}. Retrieved September 16, 2018 (\url{https://www.nytimes.com/2008/03/09/style/tmagazine/09brubach.html}).}

\hypertarget{buerkle}{Buerkle, C W. 2009. ``Metrosexuality Can Stuff It.'' \emph{Text and Performance Quarterly} 29(1):77--93.}

\hypertarget{butler}{Butler, Judith. 1990. \emph{Gender Trouble}. 1st ed. New York: Routledge.}

\hypertarget{cbs}{CBS News. 2015. \emph{Ellen Page Confronts Ted Cruz Over LGBT Rights}. Des Moines, Iowa. Retrieved May 6, 2019 (\url{https://www.youtube.com/watch?v=Iu1lsw3_Kfo}).}

\hypertarget{chan}{Chan, Eugene Y. and Natalina Zlatevska. 2019. ``Jerkies, Tacos, and Burgers: Subjective Socioeconomic Status and Meat Preference.'' \emph{Appetite} 132:257--66.}

\hypertarget{charlebois}{Charlebois, Justin. 2013. ``Herbivore Masculinity as an Oppositional Form of Masculinity.'' \emph{Culture, Society and Masculinities} 5(1):89--104.}

\hypertarget{chen}{Chen, Steven. 2012. ``The Rise of (Soushokukei Danshi) Masculinity and Consumption in Contemporary Japan.'' Pp. 283--308 in \emph{Gender, Culture, and Consumer Behavior}, edited by C. C. Otnes and L. T. Zayer. New York: Gender, Culture, and Consumer Behavior.}

\hypertarget{connell}{Connell, Raewyn. 2005. \emph{Masculinities}. Polity Press.}

\hypertarget{connell2}{Connell, Raewyn. 2017. ``Gender Relations.'' Pp. 53--75 in \emph{Gender}, \emph{Patterns in gender}.}

\hypertarget{delassio-parson}{DeLessio-Parson, Anne. 2017. ``Doing Vegetarianism to Destabilize the Meat-Masculinity Nexus in La Plata, Argentina.'' \emph{Gender, Place \& Culture} 24(12):1729--48.}

\hypertarget{fisman}{Fisman, Raymond, Sheena S. Iyengar, Emir Kamenica, and Itamar Simonson. 2006. ``Gender Differences in Mate Selection.'' \emph{Quarterly Journal of Economics} 673--97.}

\hypertarget{forchtner}{Forchtner, Bernhard and Ana Tominc. 2017. ``Kalashnikov and Cooking-Spoon: Neo-Nazism, Veganism and a Lifestyle Cooking Show on YouTube.'' \emph{Food, Culture \& Society} 20(3):415--41.}

\hypertarget{gambert}{Gambert, Iselin and Tobias Linné. 2018. ``From Rice Eaters to Soy Boys: Race, Gender, and Tropes of `Plant Food Masculinity.'' \emph{Animal Studies Journal} 7(2):129--79.}

\hypertarget{gates}{Gates, Gary J. 2011. \emph{How Many People Are Lesbian, Gay, Bisexual, and Transgender?} Los Angeles, California: The Williams Institute, UCLA School of Law.}

\hypertarget{google}{Google. 2019. ``Google Trends. `soyboy + soy boy,'\,'' April (\url{https://trends.google.com/trends/explore?date=all\&geo=US\&q=soyboy,soy\%20boy}).}

\hypertarget{greenebaum}{Greenebaum, Jessica B. 2012. ``Managing Impressions.'' \emph{Humanity \& Society} 36(4):309--25.}

\hypertarget{harney}{Harney, Alexander. 2015. ``The Herbivore's Dilemma.'' \emph{Slate}. Retrieved April 7, 2018 (\url{http://www.slate.com/articles/news_and_politics/foreigners/2009/06/the_herbivores_dilemma.html}).}

\hypertarget{hathaway}{Hathaway, Jay. 2017. ``'Soy Boys' Is the Far-Right's Newest Favorite Insult.'' \emph{The Daily Dot}. Retrieved April 24, 2019 (\url{https://www.dailydot.com/unclick/soy-boy-alt-right-insult}).}

\hypertarget{hitsch1}{Hitsch, Günter J., Ali Hortaçsu, and Dan Ariely. 2005. ``What Makes You Click: an Empirical Analysis of Online Dating.'' Working Paper, University of Chicago, Chicago, IL.}

\hypertarget{hitsch2}{Hitsch, Günter J., Ali Hortaçsu, and Dan Ariely. 2010. ``Matching and Sorting in Online Dating.'' \emph{American Economic Review} 100(1):130--63.}

\hypertarget{hollows}{Hollows, Joanne. 2003. ``Oliver's Twist.'' \emph{International Journal of Cultural Studies} 6:229--48.}

\hypertarget{hosie}{Hosie, Rachel. 2017. ``Soy Boy: What Is This New Online Insult Used by the Far Right?'' \emph{The Independent}. Retrieved April 21, 2019 (\url{http://www.independent.co.uk/life-style/soy-boy-insult-what-is-definition-far-right-men-masculinity-women-a8027816.html}).}

\hypertarget{kachel}{Kachel, Sven, Melanie C. Steffens, and Claudia Niedlich. 2016. ``Traditional Masculinity and Femininity: Validation of a New Scale Assessing Gender Roles.'' \emph{Frontiers in Psychology} 7:361--19.}

\hypertarget{kaplan}{Kaplan, Hillard, Kim Hill, Jane Lancaster, and A M. Hurtado. 2000. ``A Theory of Human Life History Evolution: Diet, Intelligence, and Longevity.'' \emph{Evolutionary Anthropology} 9(4):156--85.}

\hypertarget{khan}{Khan, Shehab. 2016. ``Writer Who Coined the Term `Herbivore Men' to Explain Japan`s Problem with Sex Speaks Out on Term's Misuse.'' \emph{Independent}. Retrieved April 7, 2018 (\url{https://www.independent.co.uk/news/world/asia/japan-sex-problem-maki-fukasawa-a7347456.html}).}

\hypertarget{kimmel}{Kimmel, Michael. 2008. \emph{Guyland: the Perilous World Where Boys Become Men}. 1st ed. London, New York: Harper Collins.}

\hypertarget{klein}{Klein, Betsy. 2019. ``Fast Food Once Again Served at White House Sports Event with Trump.'' \emph{CNN}. Retrieved April 26, 2019 (\url{https://www.cnn.com/2019/03/04/politics/trump-fast-food-white-house/index.html}).}

\hypertarget{leroy}{Leroy, Frédéric and Istvan Praet. 2015. ``Meat Traditions. The Co-Evolution of Humans and Meat.'' \emph{Appetite} 90(C):200--211.}

\hypertarget{lim}{Lim, Louisa. 2009. ``In Japan, `Herbivore' Boys Subvert Ideas of Manhood.'' \emph{NPR}. Retrieved April 7, 2018 (\url{https://www.npr.org/templates/story/story.php?storyId=120696816}).}

\hypertarget{lockie}{Lockie, Stewart and Lyn Collie. 1999. ```Feed the Man Meat.''' Pp. 255--73 in \emph{Restructuring Global and Regional Agricultures}, \emph{Gendered food and theories of consumption}, edited by D. Burch, J. Goss, and G. Lawrence. Aldershot, Hants, England, Brookfield, United States.}

\hypertarget{mcgrane}{McGrane, Sally. 2013. ``The Right-Wing Organic Farmers of Germany.'' \emph{The New Yorker}. Retrieved May 2, 2019 (\url{https://www.newyorker.com/culture/culture-desk/the-right-wing-organic-farmers-of-germany}).}

\hypertarget{millum}{Millum, Joseph. 2018. \emph{Characteristics of Self-Identified Vegetarians in the United States, 2007-2010}. Faunalytics.}
\pagebreak

\hypertarget{mooney}{Mooney, Kim M. and Erica Lorenz. 1997. ``The Effects of Food and Gender on Interpersonal Perceptions.'' \emph{Sex Roles} 36:639--53.}

\hypertarget{morioka}{Morioka, Masahiro. 2013. ``A Phenomenological Study of `Herbivore Men' Masahiro Morioka.'' \emph{The Review of Life Studies} 4:1--20.}

\hypertarget{mycek}{Mycek, Mari K. 2018. ``Meatless Meals and Masculinity: How Veg Men Explain Their Plant-Based Diets.'' \emph{Food and Foodways} 89:1--24.}

\hypertarget{nath}{Nath, Jemál. 2011. ``Gendered Fare?'' \emph{Journal of Sociology} 47(3):261--78.}

\hypertarget{neill}{Neill, Moran. 2009. ``Japan's `Herbivore Men' -\/- Less Interested in Sex, Money.'' \emph{CNN}. Retrieved April 7, 2018 (\url{http://edition.cnn.com/2009/WORLD/asiapcf/06/05/japan.herbivore.men/index.html}).}

\hypertarget{newcombe}{Newcombe, Mark A., Mary B. McCarthy, James M. Cronin, and Sinéad N. McCarthy. 2012. ```Eat Like a Man': a Social Constructionist Analysis of the Role of Food in Men's Lives.'' \emph{Appetite} 59(2):391--98.}

\hypertarget{nicolae}{Nicolae, Raluca. 2014. ``Soushoku(Kei) Danshi.'' \emph{Romanian Economic and Business Review} 9(3):66--81.}

\hypertarget{nikkhah}{Nikkhah, Roya. 2013. ``Hitler`s Food Taster Speaks of Führer's Vegetarian Diet.'' \emph{The Telegraph}. Retrieved May 2, 2019 (\url{https://www.telegraph.co.uk/history/world-war-two/9859294/Hitlers-food-taster-speaks-of-Fuhrers-vegetarian-diet.html}).}

\hypertarget{otagaki}{Otagaki, Yumi. 2009. ``Japan's `Herbivore' Men Shun Corporate Life, Sex.'' \emph{Reuters}. Retrieved April 7, 2018 (\url{https://www.reuters.com/article/us-japan-herbivores/japans-herbivore-men-shun-corporate-life-sex-idUSTRE56Q0C220090727}).}

\hypertarget{oxford}{Oxford University Press. n.d. ``Cuck.'' \emph{Oxford Dictionaries}. Retrieved April 23, 2019 (\url{https://en.oxforddictionaries.com/definition/cuck}).}

\hypertarget{p}{P, Charlier, Weil R, Rainsard P, Poupon J, and Brisard J C. 2018. ``The Remains of Adolf Hitler: a Biomedical Analysis and Definitive Identification.'' \emph{European Journal of Internal Medicine} 54:e10--e12.}

\hypertarget{pearce}{Pearce, Lisa D. 2002. ``Integrating Survey and Ethnographic Methods for Systematic Anomalous Case Analysis.'' \emph{Sociological Methodology} 32(2):103--32.}

\hypertarget{reinhart}{Reinhart, R J. 2019. ``Snapshot: Few Americans Vegetarian or Vegan.'' \emph{Gallup}. Retrieved April 7, 2019 (\href{https://news.gallup.com/poll/238328/snapshot-few-americans-vegetarian-ve-gan.aspx}{https://news.gallup.com/poll/238328/snapshot-few-americans-vegetarian-vegan.aspx}).}

\hypertarget{roos}{Roos, Gun, Ritva Prättälä, and Katriina Koski. 2001. ``Men, Masculinity and Food.'' \emph{Appetite} 37(1):47--56.}

\hypertarget{rothgerber}{Rothgerber, Hank. 2012. ``Real Men Don't Eat (Vegetable) Quiche: Masculinity and the Justification of Meat Consumption.'' \emph{Psychology of Men \& Masculinity} 14(4):363--75.}

\hypertarget{rothman}{Rothman, Lauren. 2018. ``Men Are Embarrassed to Order Vegetarian Food, British Study Finds.'' \emph{VICE}.}

\hypertarget{ruby}{Ruby, Matthew B. and Steven J. Heine. 2011. ``Meat, Morals, and Masculinity.'' \emph{Appetite} 56(2):447--50.}

\hypertarget{schosler}{Schösler, Hanna, Joop de Boer, Jan J. Boersema, and Harry Aiking. 2015. ``Meat and Masculinity Among Young Chinese, Turkish and Dutch Adults in the Netherlands.'' \emph{Appetite} 89:152--59.}

\hypertarget{sell}{Sell, Aaron, Aaron W. Lukazsweski, and Michael Townsley. 2017. ``Cues of Upper Body Strength Account for Most of the Variance in Men's Bodily Attractiveness.'' \emph{Proceedings of the Royal Society B: Biological Sciences} 284(1869):20171819--8.}

\hypertarget{shackelford}{Shackelford, Todd K., David P. Schmitt, and David M. Buss. 2005. ``Universal Dimensions of Human Mate Preferences.'' \emph{Personality and Individual Differences} 39(2):447--58.}

\hypertarget{simpson}{Simpson, Mark. 2002. ``Meet the Metrosexual.'' \emph{Salon}. Retrieved April 26, 2019 (\href{http://salon.com/2002/07/22/metrosexual}{salon.com/2002/07/22/metrosexual}).}

\hypertarget{sobal}{Sobal, Jeffery. 2006. ``Men, Meat, and Marriage.'' \emph{Food and Foodways} 13(1-2):135--58.}

\hypertarget{stenberg}{Stenberg, Alyssa. 2017. ``Vegan Men Speak Out!'' Masters dissertation, Department of Sociology, California State University. Retrieved from ProQuest Dissertations \& Theses Database, 10272359.}

\pagebreak

\hypertarget{thomas}{Thomas, Margaret A. 2015. ``Are Vegans the Same as Vegetarians? the Effect of Diet on Perceptions of Masculinity.'' \emph{Appetite} 97:79--86.}

\hypertarget{ulaby}{Ulaby, Neda. 2014. ``For These Vegans, Masculinity Means Protecting the Planet.'' \emph{All Things Considered} 5:59(1):1--3.}

\hypertarget{vandello}{Vandello, Joseph A. and Jennifer K. Bosson. 2013. ``Hard Won and Easily Lost: a Review and Synthesis of Theory and Research on Precarious Manhood.'' \emph{Psychology of Men \& Masculinity} 14(2):101--13.}

\hypertarget{vinik}{Vinik, Danny. 2019. ``A \$60 Million Pork Kickback?'' \emph{Politico} 1--5. Retrieved April 26, 2019 (\href{http://politico.com/agenda/story/2015/08/a-60-million-pork-kickback-000210}{politico.com/agenda/story/2015/08/a-60-million-pork-kickback-000210}).}

\hypertarget{woodvine}{Woodvine, Amanda. 2009. ``The Protein Myth.'' \emph{VivaHealth}. Retrieved April 25, 2019 (\url{https://www.vivahealth.org.uk/sites/default/files/Protein-vegetarian-vegan.pdf}).}

\hypertarget{yang}{Yang, Alan. 2011. ``Go Big or Go Home.'' \emph{Parks and Recreation}. edited by D. Holland. NBC.}

\hypertarget{zink}{Zink, Katherine D. and Daniel E. Lieberman. 2016. ``Impact of Meat and Lower Palaeolithic Food Processing Techniques on Chewing in Humans.'' \emph{Nature} 531(7595):500--503.}

\hypertarget{2019a}{2019a. ``Hall of Famers.'' \emph{Meat Industry Hall of Fame} Retrieved November 24, 2019 (\url{https://www.provisioneronline.com/meat-industry-hall-of-fame/hall-of-fame-winner-bios}).}

\hypertarget{2019b}{2019b. ``Urban Dictionary: Soy Boy.'' \emph{Urban Dictionary}. Retrieved April 21, 2019b {\url{https://www.urbandictionary.com/define.php?term=Soy\%20Boy\&page=5}}.}
